Benchmarking on Rigetti architecture

### 2022-10-06 txt/manuscript.tex
native gates adding

\subsection{Generic case}
Now we present the circuits for the generic case.
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-None}
\caption{Circuit representing state preparation in the  generic case.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-None}
\caption{Circuit representing $U^\dagger$ in the generic case.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-None}
\caption{Circuit representing $V_0^\dagger$ in the generic case.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-None}
\caption{Circuit representing controlled $V_0$ and $V_1$ the generic case.}
\end{figure}

@@

\subsection{IBMQ}

\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-ibmq}
\caption{Circuit representing state preparation for IBMQ.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-ibmq}
\caption{Circuit representing $U^\dagger$ for IBMQ.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-ibmq}
\caption{Circuit representing $V_0^\dagger$ for IBMQ.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-ibmq}
\caption{Circuit representing controlled $V_0$ and $V_1$ for IBMQ.}
\end{figure}

\subsection{Lucy}

\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-lucy}
\caption{Circuit representing state preparation for Lucy.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-lucy}
\caption{Circuit representing $U^\dagger$ for Lucy.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-lucy}
\caption{Circuit representing $V_0^\dagger$ for Lucy.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-lucy}
\caption{Circuit representing controlled $V_0$ and $V_1$ for Lucy.}
\end{figure}

\subsection{Rigetti}

\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-rigetti}
\caption{Circuit representing state preparation for Rigetti.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-rigetti}
\caption{Circuit representing $U^\dagger$ for Rigetti.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-rigetti}
\caption{Circuit representing $V_0^\dagger$ for Rigetti.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-rigetti}
\caption{Circuit representing controlled $V_0$ and $V_1$ for Rigetti.}
\end{figure}

>>>>

\subsection{Generic case}
Now we present the circuits for the generic case.
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/state_preparation-None}
\caption{Circuit representing state preparation in the  generic case.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/u_dag-None}
\caption{Circuit representing $U^\dagger$ in the generic case.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/v0_dag-None}
\caption{Circuit representing $V_0^\dagger$ in the generic case.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/controlled_v0_v1_dag-None}
\caption{Circuit representing controlled $V_0$ and $V_1$ the generic case.}
\end{figure}

@@

\subsection{IBMQ}
 basis gates = ["cx", "i", "rz", "sx", "x"]
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/state_preparation-ibmq}
\caption{Circuit representing state preparation for IBMQ.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/u_dag-ibmq}
\caption{Circuit representing $U^\dagger$ for IBMQ.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/v0_dag-ibmq}
\caption{Circuit representing $V_0^\dagger$ for IBMQ.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/controlled_v0_v1_dag-ibmq}
\caption{Circuit representing controlled $V_0$ and $V_1$ for IBMQ.}
\end{figure}

\subsection{Lucy}
 basis gates  =["ecr", "i", "rz", "sx", "x"] 
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/state_preparation-lucy}
\caption{Circuit representing state preparation for Lucy.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/u_dag-lucy}
\caption{Circuit representing $U^\dagger$ for Lucy.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/v0_dag-lucy}
\caption{Circuit representing $V_0^\dagger$ for Lucy.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/controlled_v0_v1_dag-lucy}
\caption{Circuit representing controlled $V_0$ and $V_1$ for Lucy.}
\end{figure}

\subsection{Rigetti}
 basis gates = ["cz", "rx", "rz"]
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/state_preparation-rigetti}
\caption{Circuit representing state preparation for Rigetti.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/u_dag-rigetti}
\caption{Circuit representing $U^\dagger$ for Rigetti.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/circuit-qiskit/v0_dag-rigetti}
\caption{Circuit representing $V_0^\dagger$ for Rigetti.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=0.8]{pics/circuit-qiskit/controlled_v0_v1_dag-rigetti}
\caption{Circuit representing controlled $V_0$ and $V_1$ for Rigetti.}
\end{figure}
